---
title: "Figures"
author: "Selina Lepori"
date: "2022-09-06"
output: html_document
---

```{r}
library(ggplot2)
library(datetime)
library(tidyr)
library(readxl)
library(ggpubr)
library(MASS)
library(MuMIn)
library(agricolae)
library(stringr)
library(nlme)
library(stats)
library(car)
require(vegan)
require(grid)
library(cowplot)
library(readr)
library(scales)
```

#######################################################################################################################
Read data
```{r}
micro <- read_excel("Masterfile.xlsx", range = "A1:CY33")

#put together the two independent variables
micro$com_moist <- str_c(micro$Community, '.', micro$moist)

##make separate files per Community
BFcomplex <- subset(micro, Community == "BFcomplex")
BFsimple <- subset(micro, Community == "BFsimple")
Bonly <- subset(micro, Community == "Bonly")
Fonly <- subset(micro, Community == "Fonly")
```

Function for Boxplots
```{r}
fct_boxplot <- function(y_of_choice, y_label, ymax, x_label, with_moisture=TRUE, y_log=TRUE, desired_ticks) {
  
  if (with_moisture==FALSE) {
    geom_boxplot = geom_boxplot(aes(x = Community, y = y_of_choice, fill = Community))
    labs = labs(y = y_label, x = x_label) 
  }
  else {
    geom_boxplot = geom_boxplot(aes(x = Community, y = y_of_choice, fill = Community, linetype = Treatment))
    labs = labs(y = y_label, x = x_label, linetype = "Moisture Treatment")
  }
  
  if (y_log==FALSE) {
    y_log = scale_y_continuous()
  }
  else { 
    y_log = scale_y_continuous(breaks = log(desired_ticks), labels = desired_ticks)
    y_of_choice = log(y_of_choice)
  }
  

  gg_boxplot <- ggplot(data = micro) +
  geom_boxplot +
  labs +
  scale_fill_manual(values = c("#CC6666", "#C4961A", "#009E73", "#D16103"), guide = "none") +
  ylim(0, ymax) +
  y_log +
  theme_bw()  +
  theme(legend.position = "none", axis.title = element_text(size = 15),
        axis.title.x=element_blank(), legend.text = element_text(size = 15),
        legend.title = element_text(size = 15))
  return(gg_boxplot)
}

fct_boxplot_moisture <- function(y_of_choice, y_label, ymax, x_label) {
  gg_boxplot <- ggplot(data = micro) +
  geom_boxplot(aes(x = Treatment, y = y_of_choice, fill = Community)) +
  labs(y = y_label, x = x_label) +
  facet_wrap(~Community) +
  scale_fill_manual(values = c("#CC6666", "#C4961A", "#009E73", "#D16103"), guide = "none") +
  ylim(0, ymax) +
  stat_compare_means(method = "t.test", aes(x = Treatment, y = log(y_of_choice)), label.x = 1, label.y = log(11000)) +
  theme_bw()  +
  theme(legend.position = "none", axis.title = element_text(size = 15),
        legend.text = element_text(size = 15), legend.title = element_text(size = 15))
  return(gg_boxplot)
}
```

Tukey Test Function
```{r}
fct_tukey <- function(y_of_choice, with_moisture=TRUE) {
  
  if (with_moisture==FALSE) {
    parametres = micro$Community
  }
  else {
    parametres = micro$com_moist
  }
  
  aov <- aov(data=micro, log(y_of_choice) ~ factor(parametres))
  summary(aov)

  df<-df.residual(aov)
  MSerror<-deviance(aov)/df
  Tukey_CM<-HSD.test(log(y_of_choice), parametres, df, MSerror, group=TRUE)
  return(Tukey_CM)
}
```

Function Scatterplot
```{r}
fct_scatterplot <- function(y_of_choice, ylabel, x_of_choice, xlabel, reg_line, desired_ticks) {
  gg_scatterplot <-
    ggplot(data = micro, aes(y = log(y_of_choice), x = x_of_choice, colour = Community)) +
    geom_point(size = 3) +
    scale_colour_manual(values = c("#CC6666", "#C4961A", "#009E73", "#D16103"), guide = "none") +
    facet_grid(~Community, labeller =
                 labeller(Community = c("BFcomplex" = "(Previous) BFcomplex",
                                        "BFsimple" = "(Previous) BFsimple",
                                        "Bonly" = "(Previous) Bonly",
                                        "Fonly" = "(Previous) Fonly"))) +
    ylim(0, NA) +
    reg_line +
    labs(y = ylabel, x = xlabel) +
    scale_y_continuous(
      breaks = log(desired_ticks),
      labels = desired_ticks) +
    stat_cor(data = micro,
             aes(y = log(y_of_choice), x = x_of_choice,
                 label=paste(..rr.label..,..p.label.., sep = "~`,`~")),
             colour = "black") +
    theme_bw() +
    theme(legend.position = "none", axis.title.y = element_text(size = 7), axis.title.x = element_text(size = 15),
          legend.text = element_text(size = 15), legend.title = element_text(size = 15))
  return(gg_scatterplot)
}
```

Cumulative Respiration: Boxplot
```{r}
gg_cum_C_h1 = fct_boxplot(y_of_choice = micro$cum_C_h1_ng, y_label = expression(paste("Cumulative Respiration (ng C soil g"^"-1", " h"^"-1",")")), ymax = NA, x_label = "Community", with_moisture=FALSE, y_log=FALSE, desired_ticks=NA)

gg_cum_C_h1_moisture = fct_boxplot_moisture(micro$cum_C_h1_ng, expression(paste("Cumulative Respiration Rate (ng C soil g"^"-1", "h"^"-1",")")), NA, "Moisture Treatment")

gg_cum_resp <- ggarrange(gg_cum_C_h1, gg_cum_C_h1_moisture, nrow=1, ncol=2, labels = c("A", "B"))

fct_tukey(micro$cum_C_h1_ng, with_moisture = FALSE)

ggsave("gg_cum_C_h_FMSOC_20231230.png", plot = gg_cum_resp, dpi=1200)
```

AAE
```{r}
gg_AAE = fct_boxplot(y_of_choice = micro$AAE_total_perc, y_label = 'Amino Sugar Accumulation Efficiency (AAE (%))', ymax = NA, x_label = "Community", with_moisture=FALSE, y_log=FALSE, desired_ticks=NA)

fct_tukey(micro$AAE_total_perc, with_moisture=FALSE)

ggsave("gg_AAE_20231230.png", plot = gg_AAE, width=16, height=13, units="cm", dpi=1200)
```


CUE Plot
```{r}
desired_ticks_resp = c(0, 5000, 20000)
desired_ticks_growth = c(0, 100, 300)
desired_ticks_CUE = c(0, 10, 30)

gg_CUE <- ggarrange(
  fct_boxplot(y_of_choice = micro$resp_h1, y_label = expression(paste("Respiration\n(ng C soil g"^"-1", " h"^"-1",")")), ymax = NA, x_label = NA, desired_ticks = desired_ticks_resp),
  fct_boxplot(y_of_choice = micro$growth1, y_label = expression(paste("Growth\n(ng C soil g"^"-1", " h"^"-1",")")), ymax = NA, x_label = NA,  desired_ticks = desired_ticks_growth),
  fct_boxplot(y_of_choice = micro$CUE1, y_label = "\nCUE (%)", ymax = NA, x_label = NA, desired_ticks = desired_ticks_CUE),
  nrow = 3, ncol = 1, heights = 1, align = "v", common.legend = TRUE, legend = "bottom", labels = c("A", "B", "C"))

# ggsave("gg_CUE_FMSOC_20231229.png", plot = gg_CUE, width=16, height=13, units="cm", dpi=1200)

#Tukey Test
fct_tukey(micro$resp_h1)
fct_tukey(micro$growth1)
fct_tukey(micro$CUE1)
```

Plot bacterial, fungal and total AS
```{r}
# gg_AS2 <- ggarrange(
#   fct_boxplot(micro$MurN_C2, expression(paste("Bacterial (µg C g soil"^"-1",")")), 20, "Community", y_log=FALSE, desired_ticks = NA),
#   fct_boxplot(micro$GlcN_f_C2, expression(paste("Fungal (µg C g soil"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
#   fct_boxplot(micro$AS_C2, expression(paste("Total (μg C soil g"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
#   nrow = 3, ncol = 1, heights = 1, align = "v", common.legend = TRUE, legend = "bottom", labels = c("E", "F", "G"))
# 
# ggsave("gg_AS2_20231230.png", plot = gg_AS2, width=16, height=13, units="cm", dpi=1200)

#Tukey Test
# fct_tukey(micro$MurN_C2)
# fct_tukey(micro$GlcN_f_C2)
fct_tukey(micro$AS_C2, with_moisture=FALSE)
```


Plot all AS
```{r}
gg_AS3 <- ggarrange(
  fct_boxplot(micro$GlcN_C2, expression(paste("GlcN (μg C soil g"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
  fct_boxplot(micro$ManN_C2, expression(paste("ManN (μg C soil g"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
  fct_boxplot(micro$GalN_C2, expression(paste("GalN (μg C soil g"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
  fct_boxplot(micro$MurN_C2, expression(paste("MurN (μg C soil g"^"-1",")")), NA, "Community", y_log=FALSE, desired_ticks = NA),
  nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom", labels = c("A", "B", "C", "D"))

# ggsave("gg_AS3_20231230.png", plot = gg_AS3, width=16, height=13, units="cm", dpi=1200)

#Tukey Test
fct_tukey(micro$GlcN_C2)
fct_tukey(micro$ManN_C2)
fct_tukey(micro$GalN_C2)
fct_tukey(micro$MurN_C2)
```

#######################################################################################################################
Amino Sugars
Plot AS (FMSOC) with CUE, resp CUE, Growth CUE, Cumulative C (PSOC)
```{r}
desired_ticks_cum_resp <- c(0, 500, 1000, 2000, 4000, 8000)
desired_ticks_growth <- c(0, 10, 25, 100, 300)
desired_ticks_resp <- c(0, 200, 1000, 10000)
desired_ticks_CUE <- c(0, 1, 5, 10, 20, 40)

p.vals = sapply(unique(micro$Community), function(i) {
  coef(summary(lm(log(cum_C_h2_ng) ~ AS_C2, data=micro[micro$Community==i, ])))[2,4]
})
reg_line_cum_C_h2 <- geom_smooth(data=micro[micro$Community %in% names(p.vals)[p.vals < 0.05],], 
                        aes(x=AS_C2, y=log(cum_C_h2_ng), colour=Community), method='lm',
               colour = "#3366FF")

p.vals = sapply(unique(micro$Community), function(i) {
  coef(summary(lm(log(growth2) ~ AS_C2, data=micro[micro$Community==i, ])))[2,4]
})
reg_line_growth2<- geom_smooth(data=micro[micro$Community %in% names(p.vals)[p.vals < 0.05],], 
                        aes(x=AS_C2, y=log(growth2), colour=Community), method='lm',
               colour = "#3366FF")

p.vals = sapply(unique(micro$Community), function(i) {
  coef(summary(lm(log(resp_h2) ~ AS_C2, data=micro[micro$Community==i, ])))[2,4]
})
reg_line_resp_h2<- geom_smooth(data=micro[micro$Community %in% names(p.vals)[p.vals < 0.05],], 
                        aes(x=AS_C2, y=log(resp_h2), colour=Community), method='lm',
               colour = "#3366FF")

p.vals = sapply(unique(micro$Community), function(i) {
  coef(summary(lm(log(CUE2) ~ AS_C2, data=micro[micro$Community==i, ])))[2,4]
})
reg_line_CUE2<- geom_smooth(data=micro[micro$Community %in% names(p.vals)[p.vals < 0.05],], 
                        aes(x=AS_C2, y=log(CUE2), colour=Community), method='lm',
               colour = "#3366FF")

gg_AS <- ggarrange(
  fct_scatterplot(micro$cum_C_h2_ng, expression(paste("Cumulative Respiration (ng C g"^"-1", " h"^"-1",")")), micro$AS_C2, "", reg_line_cum_C_h2, desired_ticks_cum_resp),
  fct_scatterplot(micro$growth2, expression(paste("Growth (ng C soil g"^"-1", " h"^"-1",")")), micro$AS_C2, "", reg_line_growth2, desired_ticks_growth),
  fct_scatterplot(micro$resp_h2, expression(paste("Respiration (ng C soil g"^"-1", " h"^"-1",")")), micro$AS_C2, "", reg_line_resp_h2, desired_ticks_resp),
  fct_scatterplot(micro$CUE2, "CUE (%) PSOC", micro$AS_C2,
                       expression(paste("Total Amino Sugars (μg C soil g"^"-1",") FMSOC")),
                                        reg_line_CUE2, desired_ticks_CUE), ncol = 1, nrow = 4)

# ggsave("gg_AS_20230717.png", plot = gg_AS)
```


#######################################################################################################################
Heatmap
Read in data
```{r, echo=FALSE}
d <- read.csv("frame2_FMSOC_not_div_TOC.csv")

d <- subset(d, select = -oldID)
```

modification of data
```{r, echo=FALSE}
##get relative signal at different temperatures rather than absolute
d[,c(1:451)]<-decostand(d[,c(1:451)], MARGIN = 1, method="total")

##separate FMSOC and PSOC
FMSOC <- d[c(1:32),]
```

Separate by RE and other soil/microbial factors
```{r, echo=FALSE}
#FMSOC
re_FM<-FMSOC[,c(1:451)]
AS_FM<-FMSOC[,c(452:457)]
# Community_FM<-FMSOC[,c(458:461)]
```

loop through and determine spearman correlations and p-values between variables
```{r}
##FMSOC
outframe_FM<-matrix(rep(NA,47100),ncol=4)

fct <- function(FM) {
  i<-1
  for(temp in 1:ncol(re_FM)){
    for(ofact in 1:ncol(FM)){
      var1<-re_FM[,temp]
      var2<-FM[,ofact]
      corval<-cor.test(var1, var2, method = "spearman")
      outframe_FM[i,]<-c(names(re_FM)[temp],names(FM)[ofact],corval$estimate, corval$p.value)
      i<-i+1
    }
  }
  return(outframe_FM)
}

outframe_FM_AS <- fct(FM = AS_FM)
# outframe_FM_Community <- fct(FM = Community_FM)
```

Reformat so the numbers are numbers and extra NAs are removed etc.
```{r}
##FMSOC
fct <- function(outframe_FM) {
  outframe_FM<-as.data.frame(outframe_FM)
  names(outframe_FM)<-c("RockEvalTemp", "variable", "Spearmancorrelation", "pvalue")
  outframe_FM$RockEvalTemp<-gsub("X", "", outframe_FM$RockEvalTemp)
  outframe_FM$RockEvalTemp<-as.numeric(as.character(outframe_FM$RockEvalTemp))
  outframe_FM$Spearmancorrelation<-as.numeric(as.character(outframe_FM$Spearmancorrelation))
  outframe_FM$pvalue<-as.numeric(as.character(outframe_FM$pvalue))
  outframe_FM<-subset(outframe_FM, !is.na(variable))
  return(outframe_FM)
}

outframe_FM_AS <- fct(outframe_FM = outframe_FM_AS)
# outframe_FM_Community <- fct(outframe_FM = outframe_FM_Community)
```

Heatmap FMSOC
```{r heatmap2, echo=FALSE, warning=FALSE}
fct <- function(outframe_FM) {
  outframe_FM$Spearmancorrelation_sig<-ifelse(outframe_FM$pvalue>=0.05,NA, outframe_FM$Spearmancorrelation)
  
  heatmap <- ggplot(outframe_FM, aes(x=RockEvalTemp, y=variable, fill=Spearmancorrelation_sig)) +
    geom_tile() +
    labs(x = "Temperature Rock-Eval Pyrolysis", y = "Variables",
         fill = "Correlation") +
    scale_fill_gradient2(low="red", mid="white", high="blue", na.value = "grey90") +
    theme(axis.title = element_text(size = 12), legend.text = element_text(size = 10),
          legend.title = element_text(size = 10), axis.text = element_text(size=10))
  
  return(heatmap)
}

heatmap_AS <- fct(outframe_FM = outframe_FM_AS)
# heatmap_Community <- fct(outframe_FM = outframe_FM_Community)
```

#######################################################################################################################
Physical Density
```{r}
#without dry treatment
PD2 <- subset(micro, moist != "D" & Community != "BFsimple")
#PD2 <- subset(PD2, Community != "BFsimple")
PD2_f <- subset(PD2, GlcN_f != 0)

gg_PD <- ggplot(data = PD2) +
  geom_point(aes(x = meso, y = AS_abs, colour = Community)) +
  scale_colour_manual(values = c("#CC6666", "#009E73", "#D16103"), guide = "none") +
  labs(x = "Mesodensity Fraction in %", y = expression(paste("Total Amino Sugars (soil g"^"-1",")"))) +
  geom_smooth(method = lm, aes(y = AS_abs, x = meso), linetype = "dashed") +
  stat_cor(data = PD2, aes(x = meso, y = AS_abs, label=paste(..rr.label.., ..p.label.., sep = "~`,`~")), colour = "black", label.y = 300) +
  theme_bw() +
  theme(axis.title = element_text(size = 12), legend.text = element_text(size = 10),
        legend.title = element_text(size = 10), axis.text = element_text(size=10))

gg_PD_f <- ggplot(data = PD2_f) +
  geom_point(aes(y = GlcN_f, x = meso, colour = Community)) +
  scale_colour_manual(values = c("#CC6666", "#D16103"), guide = "none") +
  labs(x = "Mesodensity Fraction in %", y = expression(paste("Fungal Amino Sugars (soil g"^"-1",")"))) +
  geom_smooth(method = lm, aes(y = GlcN_f, x = meso)) +
  stat_cor(data = PD2_f, aes(x = meso, y = GlcN_f, label=paste(..rr.label.., ..p.label.., sep = "~`,`~")), colour = "black", label.y = 300) +
  theme_bw() +
  theme(axis.title = element_text(size = 12), axis.text = element_text(size=10))

# PD_plot <- ggarrange(gg_PD, gg_PD_f, nrow=2)
# PD_plot <- annotate_figure(PD_plot, rot = 90, vjust = 1, size = 10)

# gg_heatmap_PD_AS <- ggarrange(heatmap_AS, gg_PD, gg_PD_f, ncol=2, nrow=2, labels = c("A", "C", "B", "D"))

# ggsave("gg_heatmap_PD_Community_20231230.png", plot = gg_heatmap_PD, width=30, height=13, units="cm", dpi=1200)
```

#######################################################################################################################
Correlation Plot fungal AS and contribution C at temperature A4 and A5
```{r}
AS_f <- subset(micro, GlcN_f != 0)

gg_AS_f_Cont_A4_A5 <- ggplot(data = AS_f) +
  geom_point(aes(x = (Contrib.A4_1 + Contrib.A5_1), y = GlcN_f, colour = Community)) +
  scale_colour_manual(values = c("#CC6666", "#C4961A", "#D16103"), guide = "none") +
  labs(y = expression(paste("Fungal Amino Sugars (soil g"^"-1",")")), x = "Contribution A4 and A5 (%)") +
  geom_smooth(method = lm, aes(x = (Contrib.A4_1 + Contrib.A5_1), y = GlcN_f)) +
  stat_cor(data = AS_f, aes(y = GlcN_f, x = (Contrib.A4_1 + Contrib.A5_1), label=paste(..rr.label.., ..p.label.., sep = "~`,`~")), colour = "black", label.y = 250) +
  #xlim(0, NA) +
  theme_bw() +
  theme(axis.title = element_text(size = 12), axis.text = element_text(size=10))

gg_AS_Cont_A4_A5 <- ggplot(data = micro) +
  geom_point(aes(x = (Contrib.A4_1 + Contrib.A5_1), y = AS_abs, colour = Community)) +
  scale_colour_manual(values = c("#CC6666", "#C4961A", "#009E73", "#D16103")) +
  labs(y = expression(paste("Total Amino Sugars (soil g"^"-1",")")), x = "Contribution A4 and A5 (%)") +
  geom_smooth(method = lm, aes(x = (Contrib.A4_1 + Contrib.A5_1), y = AS_abs), linetype = "dashed") +
  stat_cor(data = micro, aes(y = AS_abs, x = (Contrib.A4_1 + Contrib.A5_1), label=paste(..rr.label.., ..p.label.., sep = "~`,`~")), colour = "black", label.y = 250) +
  #xlim(0, NA) +
  theme_bw() +
  theme(axis.title = element_text(size = 12), axis.text = element_text(size=10))

gg_AS_fungal <- ggarrange(gg_AS_f_Cont_A4_A5 + rremove("ylab"), gg_PD_f + rremove("ylab"), ncol=1, nrow=2, labels = c("B"))
gg_AS_fungal <- annotate_figure(gg_AS_fungal, left = text_grob(expression(paste("Fungal Amino Sugars (soil g"^"-1",")")), rot = 90, vjust = 1, size = 12))
gg_AS_total <- ggarrange(gg_AS_Cont_A4_A5 + rremove("ylab"), gg_PD + rremove("ylab"), ncol=1, nrow=2, labels = c("C"))
gg_AS_total <- annotate_figure(gg_AS_total, left = text_grob(expression(paste("Total Amino Sugars (soil g"^"-1",")")), rot = 90, vjust = 1, size = 12))
gg_AS_PD <- ggarrange(gg_AS_fungal, gg_AS_total, ncol=2, nrow=1)

gg_heatmap_PD_AS <- ggarrange(heatmap_AS, gg_AS_PD, ncol=1, nrow=2, labels = c("A"))

ggsave("figures/gg_heatmap_AS_PD.png", plot = gg_heatmap_PD_AS)
```

#######################################################################################################################
Variance Partitioning
Look at the CUE (PSOC) and the variance explained by AS_C2, MBC1, A1+A2_PSOM, A4+A5_PSOM.
```{r}
rda_CUE2 <- vegan::rda(micro$growth2 ~ AS_C2 + MBC1 + Contrib.A1_2 + Contrib.A2_2 + Contrib.A4_2 + Contrib.A5_2, data = micro)
#summary(rda_CUE2)
anova(rda_CUE2, by="terms", perm.max=100)

#rda_CUE2 <- step(rda_CUE2, direction = "backward")

var_CUE2 <- varpart(micro$growth2, 
                     ~ AS_C2,
                     ~ MBC1,
                     ~ Contrib.A1_2 + Contrib.A2_2,
                     ~ Contrib.A4_2 + Contrib.A5_2,
                     data = micro)
var_CUE2
#showvarparts(4)
plot(var_CUE2, cutoff = 0.001, digits = 1, cex = 0.7)
```